\documentclass{resume}

\usepackage[left=0.4in,top=0.4in,right=0.4in,bottom=0.4in]{geometry}
\usepackage{hyperref}

\name{YASH RANA}

\address{+91 81309 23346 | New Delhi, India}
\address{
\href{mailto:ranayash812@gmail.com}{ranayash812@gmail.com} | 
\href{https://linkedin.com/in/devop-yash-rana}{linkedin.com/in/devop-yash-rana} | 
\href{https://yashrana.online}{yashrana.online}
}

\begin{document}

%----------------------------------------------------------------------------------------
% OBJECTIVE SUMMARY
%----------------------------------------------------------------------------------------

\begin{rSection}{PROFESSIONAL SUMMARY}

Full Stack Engineer focused on building scalable backend systems and production-grade distributed applications. Experienced in microservices architecture, CI/CD automation, and cloud-native deployments using MERN and containerized infrastructure.

\end{rSection}

%----------------------------------------------------------------------------------------
% EDUCATION
%----------------------------------------------------------------------------------------

\begin{rSection}{EDUCATION}

\textbf{Bachelor’s of Computer Application}, Quantum University \hfill 2022 -- 2025

\end{rSection}

%----------------------------------------------------------------------------------------
% SKILLS
%----------------------------------------------------------------------------------------

\begin{rSection}{SKILLS}

\textbf{Languages:} JavaScript, TypeScript, SQL, Rust \\
\textbf{Frontend:} React.js, Next.js, Tailwind CSS \\
\textbf{Backend:} Node.js, Express.js, REST APIs, WebSockets \\
\textbf{Databases:} MongoDB, PostgreSQL, Redis \\
\textbf{DevOps \& Cloud:} Docker, AWS, CI/CD, Nginx

\end{rSection}

%----------------------------------------------------------------------------------------
% EXPERIENCE
%----------------------------------------------------------------------------------------

\begin{rSection}{EXPERIENCE}

\textbf{Full Stack Blockchain Developer} \hfill Nov 2024 -- Present \\
QuadB Technologies \hfill \textit{Ludhiana, Punjab}
\begin{itemize}
    \item Developed and deployed Rust-based smart contracts on ICP blockchain with secure transaction validation.
    \item Integrated decentralized applications with backend APIs ensuring secure data exchange.
    \item Optimized contract performance and implemented access control mechanisms for production environments.
\end{itemize}

\textbf{Full Stack Developer Intern} \hfill Oct 2023 -- Apr 2024 \\
Chainshift \hfill \textit{Greater Noida, Uttar Pradesh}
\begin{itemize}
    \item Built scalable MERN stack applications with RESTful APIs and optimized database queries.
    \item Integrated third-party APIs and backend services improving system reliability and workflow automation.
    \item Implemented CI/CD pipelines using Docker and cloud deployments for production-ready releases.
\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
% PROJECTS
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}

\textbf{Trivx AI} — Founder \& Full Stack Engineer \hfill \href{https://trivx.in}{trivx.in} \\
\textit{AI-Driven DevOps Orchestration Platform}
\begin{itemize}
    \item Built an AI-driven DevOps orchestration platform automating CI/CD pipelines and multi-cloud deployments.
    \item Designed microservices-based architecture supporting AWS, GCP, and Azure integrations.
    \item Implemented role-based access control (RBAC), usage-based billing, and real-time observability dashboard reducing manual deployment effort by 90\%.
\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
% CERTIFICATIONS
%----------------------------------------------------------------------------------------

\begin{rSection}{CERTIFICATIONS}

\begin{itemize}
    \item API Security Architect
    \item Kubernetes for Developers
\end{itemize}

\end{rSection}

\end{document}